Verifying Demonstrations

### 2021-06-16 paper/intro.tex
Breaks out outline, CANSifies intro

\paragraph{Outline}

The paper is organized as follows.
In \cref{current-crowd-counting}, we describe current crowd counting and the 
desired properties.
In \cref{definitions}, we describe our system model and formalize the notion of 
protest and the desired verifiability and privacy properties.
In \cref{building-blocks}, we give the relevant background on the building 
blocks of our solution.
%
%\Cref{DB-anon-cred}, we present a new \ac{DB} version of the Schnorr protocol, 
%different from that originally proposed by \textcite{DistanceBounding}.
%We provide a proof of its security and formally verify it using 
%Tamarin~\cite{TamarinDB}.
%
We present \CROCUS, a privacy-preserving crowd counting 
%estimation 
protocol in in \Cref{Protocol}, analyze its security in \cref{SecurityAnalysis}, and estimate its performance in \cref{PerformanceAnalysis}.
We compare it to related work in \cref{related-work}.
Finally, we discuss limitations and assumptions in \cref{Discussion} and give 
our conclusions in \cref{Conclusion}.

>>>>

\input{current-crowd-counting}
\input{outline.tex}
